The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-05-01 paper/ms.tex
Lambda values

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}

\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}   
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}   
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman $\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{f8.eps}
\end{center}
\caption{Geometry of the gas distribution. The angular velocity vector
  is parallel to the unit vector $\hat{k}$. In order to describe the
  departures from spherical symmetry we use the polar angle $\theta$
  formed by the direction of the outgoing photons with respecto to the
  $z$-axis. We define define the variable $\mu\equiv\cos\theta$ to
  report to present our results.
    \label{fig:geometry}}  
\end{figure}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{spectraCentral.eps}
\end{center}
\caption{
2D histogram showing the number of photons that escape with frecuency
$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
rotationa axis. The rotational velocity ($0,100,200,300$\kms)
increases from left to right and the optical depth ($10^5$, $10^6$,
$10^7$) from top to bottom. The \ly photons are initialized at the
center of the sphere.
\label{fig:CentralSpec} }   
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{spectraHOM.eps}
\end{center}
\caption{Same as Figure \ref{fig:CentralSpec} for \ly photons
  initialized homogeneously throughout the sphere.
    \label{fig:HomSpec}}  
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{f1.eps}
\end{center}
\caption{Shape of the \ly line for different maximum rotational
  velocities for a viewing angle perpendicular to the rotation axis
  ($|\mu|\sim 0$). The continuous (dashed) line represents the central
  (homogeneous) source distributions.  The panels follow the same
  correspondence as Figures \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{muhisto.eps}
\end{center}
\caption{Integrated flux distribution, $F(\mu)$, as a function of the
  viewing angle as parameterized by $\mu$. We show the results for the
  homogeneous source distribution in models with rotational velocities
  $0$\kms, $300$\kms and  optical depths $10^5$, $10^6$ and $10^7$. We
  see that the distribution is flat, meaning that the flux for all
  viewing angles is the same. The results for the central sources are
  similar. 
\label{fig:muhisto}}
\end{figure}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{widths.eps}
\end{center}
  \caption{FWHM for the non-dusty models as a function of the viewing
  angle parameterized by $\mu\equiv\cos\theta$. 
  Continuous (dashed) lines  correspond to central (homogeneous)
  source distributions. The general trend is of an decreasing FWHM as
  the line of sight becomes parallel to the rotation axis. 
  \label{fig:widthvsmu}} 
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{f2.eps}
\end{center}
\caption{FWHM for the non-dusty models as a function of
  rotational velocity $V_{\rm max}$. The left panel shows the
  results in velocity units while the right panel normalizes
  the data by the FWHM in the static case. 
  Continuous (dashed) lines  correspond to central (homogeneous)
  source distributions. The straight lines represent the fit to
  the data using the expression in Eq. (\ref{eq:fwhm}).
  \label{fig:widthsvsvelocity}}
\end{figure*}

@@

With this test we want to know to what extent the new velocity width
can be expressed as a quadratic sum of the two relevant velocities in
the problem. We fit simultaneously all the points corresponding to
central and homogeneous models to find $\lambda_{\rm c} = XX \pm
XX$ and $\lambda_{\rm h}= XX\pm XX$ respectively.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{maxima.eps}
\end{center}
\caption{Position of the line maxima as a function of maximum
  rotational   velocity $V_{\rm max}$. Continuous (dashed) lines
  correspond to   central (homogeneous) source distributions. A value
  of $x_{\rm     max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}
\end{figure*}

>>>>

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}   
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}   
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman $\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{f1.pdf}
\end{center}
\caption{Geometry of the gas distribution. The angular velocity vector
  is parallel to the unit vector $\hat{k}$. In order to describe the
  departures from spherical symmetry we use the polar angle $\theta$
  formed by the direction of the outgoing photons with respecto to the
  $z$-axis. We define define the variable $\mu\equiv\cos\theta$ to
  report to present our results.
    \label{fig:geometry}}  
\end{figure}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{f2.pdf}
\end{center}
\caption{
2D histogram showing the number of photons that escape with frecuency
$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
rotationa axis. The rotational velocity ($0,100,200,300$\kms)
increases from left to right and the optical depth ($10^5$, $10^6$,
$10^7$) from top to bottom. The \ly photons are initialized at the
center of the sphere.
\label{fig:CentralSpec} }   
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{f3.pdf}
\end{center}
\caption{Same as Figure \ref{fig:CentralSpec} for \ly photons
  initialized homogeneously throughout the sphere.
    \label{fig:HomSpec}}  
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{f4.pdf}
\end{center}
\caption{Shape of the \ly line for different maximum rotational
  velocities for a viewing angle perpendicular to the rotation axis
  ($|\mu|\sim 0$). The continuous (dashed) line represents the central
  (homogeneous) source distributions.  The panels follow the same
  correspondence as Figures \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{f5.pdf}
\end{center}
\caption{Integrated flux distribution, $F(\mu)$, as a function of the
  viewing angle as parameterized by $\mu$. We show the results for the
  homogeneous source distribution in models with rotational velocities
  $0$\kms, $300$\kms and  optical depths $10^5$, $10^6$ and $10^7$. We
  see that the distribution is flat, meaning that the flux for all
  viewing angles is the same. The results for the central sources are
  similar. 
\label{fig:muhisto}}
\end{figure}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{f6.pdf}
\end{center}
  \caption{FWHM for the non-dusty models as a function of the viewing
  angle parameterized by $\mu\equiv\cos\theta$. 
  Continuous (dashed) lines  correspond to central (homogeneous)
  source distributions. The general trend is of an decreasing FWHM as
  the line of sight becomes parallel to the rotation axis. 
  \label{fig:widthvsmu}} 
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{f7.pdf}
\end{center}
\caption{FWHM for the non-dusty models as a function of
  rotational velocity $V_{\rm max}$. The left panel shows the
  results in velocity units while the right panel normalizes
  the data by the FWHM in the static case. 
  Continuous (dashed) lines  correspond to central (homogeneous)
  source distributions. The straight lines represent the fit to
  the data using the expression in Eq. (\ref{eq:fwhm}).
  \label{fig:widthsvsvelocity}}
\end{figure*}

@@

With this test we want to know to what extent the new velocity width
can be expressed as a quadratic sum of the two relevant velocities in
the problem. We fit simultaneously all the points corresponding to
central and homogeneous models to find $\lambda_{\rm c} = 0.84 \pm
XX$ and $\lambda_{\rm h}= 0.54\pm XX$ respectively.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{f8.pdf}
\end{center}
\caption{Position of the line maxima as a function of maximum
  rotational   velocity $V_{\rm max}$. Continuous (dashed) lines
  correspond to   central (homogeneous) source distributions. A value
  of $x_{\rm     max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}
\end{figure*}
